Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-01 finaletd/mainintroduction.tex
changes

Completeness guarantees that a garbage collector will collect all garbage objects in the heap, thereby removing all memory leaks in the heap. Reference counting garbage collectors are well known for incomplete garbage collection due to their inability to collect cyclic garbage. This property is challenging as the locality-based collectors usually use reference counting. Collectors designed for both environments use reference counting and tracing echnique to solve the problem and guarantees the garbage collectors are complete.

>>>>

Completeness guarantees that a garbage collector will collect all garbage objects in the heap, thereby removing all memory leaks in the heap. Reference counting garbage collectors are well known for incomplete garbage collection due to their inability to collect cyclic garbage. This property is challenging as the locality-based collectors usually use reference counting. Collectors designed for both environments use reference counting and tracing techniques to solve the problem and guarantees the garbage collectors are complete.
